Supplementary Materials

### 2023-07-13 manuscript/supplementary.tex
ms updates

\begin{align}
  \label{eq:va_bgs}
  V_\text{BGS} &:= \V(w) = 2 s^2 \sum_{l=1}^L p_l(1-p_l) \nonumber  \\
            &= 2 L s^2 \frac{\mu}{s} \left( 1 - \frac{\mu}{s}\right) = U s + \mathcal{O}(\mu^2) \approx Us.
\end{align}
%
since under mutation-selection balance $p_l = \nicefrac{\mu}{s}$ and $U$ is
defined $U := 2 L \mu$, the deleterious mutation rate per diploid genome, per
generation. They then set $V_A = V_\text{BGS}$, and note that $V_m \approx
Us^2$, since mutations have frequency of $\nicefrac{1}{2N}$ and each increase
the variance by a factor of $s^2$. Note that because the classic BGS model
assumes deterministic selection dynamics (i.e. an infinite population), the
equilibrium $Z$ given by equation \eqref{eq:Z} excludes the reduction due to
drift. The reduction factor under the strong BGS model is,

@@

\caption{$R^2$ and mutation rate estimates for all primary models fit on the
    default DFE grid (up to selection $s=10^{-1}$).}

@@

  Feature Priority &              full &          CHB &                        55.63 &             57.88 &            51.39 &

@@

\begin{table}
    \label{supp:tbl-r2-strongsel}
\centering
\caption{$R^2$ and mutation rate estimates for all primary models fit 
    with the strong selection grid (up to $s=10^{-1}$). Note that the repeated values in the last rows are
    correct and due to rounding; see \path{notebooks/main_fits.ipynb} in the
    GitHub repository for more information.}

@@

\begin{tabular}{|l|llrr|}
\hline
Annotation Model &  Population &    Feature &   ${\bar{s}}$ (default grid) & ${\bar{s}}$ (constrained grid) \\
\hline
 PhastCons Priority &  CEU &        CDS &  0.100000 &  0.000000 \\
 PhastCons Priority &  CEU &       gene &  0.005308 &  0.000226 \\
 PhastCons Priority &  CEU &  PhastCons &  0.008076 &  0.006275 \\
 PhastCons Priority &  CHB &        CDS &  0.100000 &  0.000000 \\
 PhastCons Priority &  CHB &       gene &  0.004896 &  0.000296 \\
 PhastCons Priority &  CHB &  PhastCons &  0.001327 &  0.005886 \\
 PhastCons Priority &  YRI &        CDS &  0.000000 &  0.000000 \\
 PhastCons Priority &  YRI &       gene &  0.005556 &  0.000160 \\
 PhastCons Priority &  YRI &  PhastCons &  0.028642 &  0.007575 \\
   Feature Priority &  CEU &        CDS &  0.075041 &  0.005281 \\
   Feature Priority &  CEU &       gene &  0.001654 &  0.000315 \\
   Feature Priority &  CEU &  PhastCons &  0.069563 &  0.008767 \\
   Feature Priority &  CHB &        CDS &  0.074797 &  0.005211 \\
   Feature Priority &  CHB &       gene &  0.001974 &  0.000271 \\
   Feature Priority &  CHB &  PhastCons &  0.051988 &  0.008507 \\
   Feature Priority &  YRI &        CDS &  0.054503 &  0.001576 \\
   Feature Priority &  YRI &       gene &  0.001912 &  0.000336 \\
   Feature Priority &  YRI &  PhastCons &  0.055153 &  0.009369 \\
            CADD 6\% &  CEU &      CADD 6\% &  0.042458 &  0.006500 \\
            CADD 6\% &  CHB &      CADD 6\% &  0.031565 &  0.005733 \\
            CADD 6\% &  YRI &      CADD 6\% &  0.043671 &  0.007926 \\
            CADD 8\% &  CEU &      CADD 8\% &  0.041254 &       - \\
            CADD 8\% &  CHB &      CADD 8\% &  0.029052 &       - \\
            CADD 8\% &  YRI &      CADD 8\% &  0.046212 &       - \\
\hline
\end{tabular}

@@

>>>>

\begin{align}
  \label{supp-eq:va_bgs}
  V_\text{BGS} &:= \V(w) = 2 s^2 \sum_{l=1}^L p_l(1-p_l) \nonumber  \\
            &= 2 L s^2 \frac{\mu}{s} \left( 1 - \frac{\mu}{s}\right) = U s + \mathcal{O}(\mu^2) \approx Us.
\end{align}
%
since under mutation-selection balance $p_l = \nicefrac{\mu}{s}$ and $U$ is
defined $U := 2 L \mu$, the deleterious mutation rate per diploid genome, per
generation. They then set $V_A = V_\text{BGS}$, and note that $V_m \approx
Us^2$, since mutations have frequency of $\nicefrac{1}{2N}$ and each increase
the variance by a factor of $s^2$. Note that because the classic BGS model
assumes deterministic selection dynamics (i.e. an infinite population), the
equilibrium $Z$ given by equation \eqref{eq:Z} excludes the reduction due to
drift. The reduction factor under the strong BGS model is,

@@

\caption{$R^2$ and mutation rate estimates for all primary models fit on the
default DFE grid (up to selection $s=10^{-1}$). $R_\text{IS}^2$ is the
in-sample $R^2$, and $R_\text{LOCO}^2$ is the leave-one-chromosome-out $R^2$.}

@@

  Feature Priority &              full &          CHB &                        55.63 &             57.88 &            51.39 &                                 3.1722 &                                0.1056 \\

@@

\begin{table}
    \label{supp:tbl-r2-strongsel}
\centering

\caption{$R^2$ and mutation rate estimates for all primary models fit with the
    strong selection grid (up to $s=10^{-1}$). Note that the repeated values in
    the last rows are correct and due to rounding; see
    \path{notebooks/main_fits.ipynb} in the GitHub repository for more
information. $R_\text{IS}^2$ is the in-sample $R^2$, and $R_\text{LOCO}^2$ is
the leave-one-chromosome-out $R^2$. }

@@

\begin{tabular}{|l|llrr|}
\hline
Annotation Model &  Population &    Feature &   ${\bar{s}}$ (default grid) & ${\bar{s}}$ (constrained grid) \\
\hline
PhastCons Priority & CEU &       CDS &         0.100000 &       0.000000 \\
PhastCons Priority & CEU &      gene &         0.005308 &       0.000226 \\
PhastCons Priority & CEU & phastcons &         0.008076 &       0.006278 \\
PhastCons Priority & CHB &       CDS &         0.100000 &       0.000000 \\
PhastCons Priority & CHB &      gene &         0.004896 &       0.000296 \\
PhastCons Priority & CHB & phastcons &         0.001327 &       0.005887 \\
PhastCons Priority & YRI &       CDS &         0.000000 &       0.000000 \\
PhastCons Priority & YRI &      gene &         0.005556 &       0.000163 \\
PhastCons Priority & YRI & phastcons &         0.028642 &       0.007687 \\
  Feature Priority & CEU &       CDS &         0.075041 &       0.005284 \\
  Feature Priority & CEU &      gene &         0.001654 &       0.000315 \\
  Feature Priority & CEU & phastcons &         0.069563 &       0.008772 \\
  Feature Priority & CHB &       CDS &         0.074797 &       0.005211 \\
  Feature Priority & CHB &      gene &         0.001974 &       0.000271 \\
  Feature Priority & CHB & phastcons &         0.051988 &       0.008507 \\
  Feature Priority & YRI &       CDS &         0.054503 &       0.001576 \\
  Feature Priority & YRI &      gene &         0.001912 &       0.000336 \\
  Feature Priority & YRI & phastcons &         0.055153 &       0.009370 \\
           CADD 6\% & CEU &     cadd6 &         0.042458 &       0.006500 \\
           CADD 6\% & CHB &     cadd6 &         0.031565 &       0.005733 \\
           CADD 6\% & YRI &     cadd6 &         0.043671 &       0.007926 \\
           CADD 8\% & CEU &     cadd8 &         0.041254 &       0.006017 \\
           CADD 8\% & CHB &     cadd8 &         0.029052 &       0.005068 \\
           CADD 8\% & YRI &     cadd8 &         0.046212 &       0.007543 \\
\hline
\end{tabular}

@@

\begin{figure}[htbp]
  \label{suppfig:resid-sweeps}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/sweep_residuals.pdf}

  \caption{The distributions of residuals in windows containing hard or soft
  sweeps (blue) and not containing sweeps (orange) found by
\parencite{Schrider2017-yx}.}
